Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2024-06-22 NovelLBM.tex
review1

@@

	Here $\vec{u}$ is the local fluid velocity, $\rho$ is the local density, $w_i$ are the lattice weights associated to the chosen velocity set and $c_\text{s}$ is the lattice speed of sound defined as follows.

@@

	For forces we use the algorithm presented by Guo et al. \cite{guo2002}.  \SG{ what are ''simple forces''? }\RK{as opposed to stresses which are generalized forces. -> removed the "simple"}

@@

	Typically, one picks $\rho_\text{LU} = 1$ and $\eta_\text{LU} = \frac{1}{6}$.

@@

	A convenient third scale is the resolution, meaning the relation of $\Delta x$ to the size of the system.

@@

	\begin{equation}
		\begin{split}
			&\frac{\Delta t}{\Delta x}\vec{c}_i = \\
			&\begin{Bmatrix}
				0 & 1 & -1 & 0 & 0 & 0 & 0 & 1 & -1 & 1 & -1 & 0 & 0 & 1 & -1 & 1 & -1 & 0 & 0 \\
				0 & 0 & 0 & 1 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 & -1 & -1 & 1 & 0 & 0 & 1 & -1 \\
				0 & 0 & 0 & 0 & 0 & 1 & -1 & 0 & 0 & 1 & -1 & 1 & -1 & 0 & 0 & -1 & 1 & -1 & 1
			\end{Bmatrix}
		\end{split}
	\end{equation}
	Where each column is a vector.
	\begin{equation}
		w_i = \begin{cases}
			\frac{1}{3},\quad i=0\\
			\frac{1}{18},\quad 1 \leq i \leq 6\\
			\frac{1}{36},\quad \text{otherwise}
		\end{cases}
	\end{equation}
	}

>>>>

	We use D3Q19. Its 19 velocities can be found in equation~(\ref{eq:D3Q19c}).

@@

	Here $\vec{u}$ is the local fluid velocity, $\rho$ is the local density, $w_i$ are the lattice weights associated to the chosen velocity set (given in equation~(\ref{eq:D3Q19w}) for D3Q19) and $c_\text{s}$ is the lattice speed of sound defined as follows.

@@

	For the forces used to drive the simple periodic flows and the forces from the IBM used to simulate cells, we use the algorithm presented by Guo et al. \cite{guo2002}.  \SG{ what are ''simple forces''? }\RK{as opposed to stresses which are generalized forces. -> removed the "simple"}

@@

	We pick $\rho_\text{LU} = 1$ and $\eta_\text{LU} = \frac{1}{6}$ as is typically done.

@@

	A convenient third scale is the resolution, meaning the relation of $\Delta x$ to the size of the system, which we pick depending on the geometry.

@@

	\begin{equation}\label{eq:D3Q19c}
		\begin{split}
			&\frac{\Delta t}{\Delta x}\vec{c}_i = \\
			&\begin{Bmatrix}
				0 & 1 & -1 & 0 & 0 & 0 & 0 & 1 & -1 & 1 & -1 & 0 & 0 & 1 & -1 & 1 & -1 & 0 & 0 \\
				0 & 0 & 0 & 1 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 & -1 & -1 & 1 & 0 & 0 & 1 & -1 \\
				0 & 0 & 0 & 0 & 0 & 1 & -1 & 0 & 0 & 1 & -1 & 1 & -1 & 0 & 0 & -1 & 1 & -1 & 1
			\end{Bmatrix}
		\end{split}
	\end{equation}
	Where each column is a vector.
	\begin{equation}\label{eq:D3Q19w}
		w_i = \begin{cases}
			\frac{1}{3},\quad i=0\\
			\frac{1}{18},\quad 1 \leq i \leq 6\\
			\frac{1}{36},\quad \text{otherwise}
		\end{cases}
	\end{equation}
	}

### 2024-06-22 responses/Response1.tex
review1

\documentclass[12pt,a4paper, onesided]{article}
% !TeX program=pdflatex
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[ngerman,american]{babel}

@@

\newcommand{\SG}[1]{{\color{red}SG:~#1}}
\newcommand{\SJM}[1]{{\color{orange}SM:~#1}}
\newcommand{\SW}[1]{{\color{purple}SW:~#1}}

@@

The parameters $ \eta _0$ and $ \eta _ \infty $ are the viscosities predicted by the model for zero and  and infinite shear rates, respectively.
We now mention this just before Eq. (7).

@@

We have added a new appendix E where we discuss the LB method in general as well as our specific implementation details. 
\SG{der Appendix ist an sich ok, aber sollte noch frueher und deutlicher auf unsere Implementierung eingehen, z.B. D3Q19 bereits dort erwähnen, wo du auf velocity sets eingehst. Beim Guo forcing konkret sagen, wofuer wir es verwenden (''simple forces'' ist hier zu vage). Bei der Dichte und der Viskositaet ist es nicht so wichtig, was man ''typically'' nimmt, sondern was du konkret in deinen Simulationen genommen hast. }

@@

Our choice of the finite-volume method is motivated primarily by its clarity and simplicity when implementing complex boundary conditions.
Furthermore, the finite-volume method matches well with the so-called corner-transport-upwind (CTU) scheme which we use for advection and for which earlier works \SG{ give ref of Kuron } reported increased stability.
To make these points clearer to the reader, we added many corresponding details to section 4.2 of the revised manuscript.
%Finite difference is a lot harder to implement (boundary conditions), has a lot more loose ends to tie (to assure conservation for example) and is less stable.

@@

Man kann die Varianten auch kombinieren. Kannst du zu (ii) und (iii) mal raussuchen, was da der Stand ist?}

@@

>>>>

\documentclass[12pt,a4paper, onesided]{article}
% !TeX program=pdflatex
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[american]{babel}

@@

\newcommand{\SG}[1]{{\color{red}SG:~#1}}
\newcommand{\SJM}[1]{{\color{orange}SM:~#1}}
\newcommand{\SW}[1]{{\color{purple}SW:~#1}}
\newcommand{\RK}[1]{{\color{cyan}RK: #1}}

\usepackage[
backend=bibtex,
citestyle=numeric-comp,
maxbibnames=10,
sorting=none
]{biblatex}
\addbibresource{../assets/bib/bib.bib}

@@

The parameters $\eta_0$ and $\eta_\infty$ are the viscosities predicted by the model for zero and infinite shear rates, respectively.
We now mention this just before Eq. (7).\RK{Eigentlich beziehen sich die auf CY bzw. auf experimentelle Daten.}

@@

We have added a new appendix E where we discuss the LB method in general as well as our specific implementation details. 
\SG{der Appendix ist an sich ok, aber sollte noch frueher und deutlicher auf unsere Implementierung eingehen, z.B. D3Q19 bereits dort erwähnen, wo du auf velocity sets eingehst. Beim Guo forcing konkret sagen, wofuer wir es verwenden (''simple forces'' ist hier zu vage). Bei der Dichte und der Viskositaet ist es nicht so wichtig, was man ''typically'' nimmt, sondern was du konkret in deinen Simulationen genommen hast. }\RK{Habe deine Beispiele übernommen}

@@

Our choice of the finite-volume method is motivated primarily by its clarity and simplicity when implementing complex boundary conditions.
Furthermore, the finite-volume method matches well with the so-called corner-transport-upwind (CTU) scheme which we use for advection and for which earlier works \cite{kuron2021}\SG{ give ref of Kuron }\RK{done} reported increased stability.
To make these points clearer to the reader, we added many corresponding details to section 4.2 of the revised manuscript.
%Finite difference is a lot harder to implement (boundary conditions), has a lot more loose ends to tie (to assure conservation for example) and is less stable.

@@

Man kann die Varianten auch kombinieren. Kannst du zu (ii) und (iii) mal raussuchen, was da der Stand ist?}
\RK{
(i) Der Vorschlag ist in etwa so sinnvoll wie vorzuschlagen unsere GPUs pink anzumalen und zu schauen ob das hilft. Da wir MRT ohnehin schon implementiert haben wäre das auch deutlich einfacher gewesen als das Zeug hier zu erfinden. Das führt also mit Nichten zu weit. Mir ist ein Rätsel wie du diese Antwort für eine echte Möglichkeit halten kannst.

(ii) Wir haben es ausprobiert. Es hatte schon für die simpelsten Systeme keinerlei Effekt. Was auch wenig überraschend ist, denn wenn wir die Literatur mal eben nach Leuten durchsuchen die nicht nur nachplappern MRT würde die Stabilität verbessern sondern die raussuchen die dazu was konkretes zeigen (z.B. https://doi.org/10.1016/j.jnnfm.2011.01.002 https://ntrs.nasa.gov/api/citations/20020075050/downloads/20020075050.pdf), so stellen wir fest, dass die von Re = 100 und aufwärts reden. Bei MRT geht es um die Verbesserung der Stabilität zeigabhängiger bis turbulenter Strömungen. Das hat mit unserem Problem schlichtweg nichts zu tun, deshalb haben wir nie für irgendwas einen relevanten Effekt durch MRT gesehen.

(iii) Die Literatur die wir zitieren (Dzanic) gibt sogar an, dass MRT für ihren klassischen Ansatz nicht angemessen ist weil nicht turbulent "Although the current LB solver
uses the SRT model, which is appropriate for the
current investigation [i.e., Re $\tilde{}$ O (1)], exten-
sions to two-relaxation-time (TRT) and multiple-
relaxation-time (MRT) models are easily applica-
ble for the scheme in scenarios involving inertialess
(Re << 1) or turbulent (Re >> 1e3 ) conditions."
oder ganz allgemein zu MRT von Krüger:
"However, the simplicity and efficiency of the lattice Boltzmann
BGK collision operator comes at the cost of reduced accuracy (in particular for large
viscosities) and stability (especially for small viscosities). Multiple-relaxation-time
(MRT) collision operators offer a larger number of free parameters that can be tuned
to overcome these problems."
Die Literatur die wir zitieren (mit Ausnahme von Gupta) benutzt kein MRT (Kuron TRT rest SRT), weil MRT hier nichts verloren hat. Und Gupta rechtfertigt seine Verwendung auch nur mit "Ist besser, siehe paper das von hohen Re spricht" ohne das selbst für seinen Fall zu belegen. In unserem Literaturvergleich ist er der Schlechteste.

Wenn du möchtest, können wir gerne schreiben "haben wir ausprobiert, bringt nichts" (ich wüsste aber nicht welche Belege wir hierfür liefern sollten/müssten, die Simulation ergibt so und so nan), aber ich halte diesen "Vorschlag" für nicht angemessen und will nicht riskieren, dass dem auch noch einfällt wir könnten die ganzen Parameter ja mal durchtunen.
}

@@

\printbibliography[heading=bibintoc]
